---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

```{r echo=FALSE, results="hide", message=FALSE}
library("badger")
```

# andyHMM


<!-- badges: start -->
`r badge_lifecycle(stage = "experimental")`
<!-- badges: end -->

Basic implementation of the Hidden Markov Algorithms described in [Rabiner, 1989](https://ieeexplore.ieee.org/document/18626). Odds are: something in this package does not work as intended; use at your own risk. Currently only implements functions for discrete output models with time-homogeneous transition matrices; see package `depmixS4` for a more full-featured HMM suite.

## Functions

* `simulate_hmm`: simulate sequence of observations (x) and hidden states (z) for a simple HMM defined by an initial probability vector (pi), an NxN transition matrix (A), and a NxK emission probability matrix (B)
* `forward_algorithm`: for a given HMM and a sequence of observations, compute the likelihood of the observed sequences (integratin over the set of all possible underlying hidden states)
* `viterbi` and `viterbi_log`: For a given HMM and sequence of observed states compute the most likely sequence of underlying hidden states. `viterbi_log` uses log-probabilities in its calculations
* `update_parameters`: run one iteration of the Baum-Welch algorithm to update parameter estimates for a HMM


